---
output: github_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(out.width = 830, out.height = 415)
```

# Imgix

[`{htmlwidgets}`] bindings for the [imgix rendering API].
Use images from the API in your [`{shiny}`] apps and [`{rmarkdown}`] documents.

## Installation

This package can be installed directly from github using the [`{remotes}`] package

```r
remotes::install_github("r-webutils/imgix")
```

## Usage

Images can be defined with the `imgx()` function.
You can either enter a full URL or an id from https://pexels.com.

```{r}
library(imgix)
imgix(2339009)
imgix("https://images.unsplash.com/photo-1459478309853-2c33a60058e7")
```

## API Parameters

API parameters can be passed directly to `imgix()`.
Underscores are automatically converted to hyphens.

```{r}
imgix(2422497, rot = 30)
imgix(1529360, txt = "Enjoy the rain", txt_size = 100, txt_color = "ddd", 
       txt_align = "center,middle", blur = 20)
```

## Shiny

Use `renderImgix()` to include images to your shiny application.

```r
output$imgix <- renderImgix({
  imgix_as_widget(imgix(2339009))
})
```

The sizing must be defined in the corresponding output function `imgixOutput()`.

## Rendering Modes

This packages uses three different strategies to render images depending on
the context. 

#### Mode 1: htmlwidget

The default mode.
The widget is shown using the [`{htmlwidgets}`] interface.
Typical usecases are shiny applications and the rstudio viewer pane.
Use `imgix_as_widget()` to directly generate the widget object.

```{r}
widget <- imgix_as_widget(imgix(2339009))
```

#### Mode 2: html tag

The image is rendered to an html tag using the [`{htmltools}`] package.
The `htmltools::as.tag()` generic is implemented and returns an `<img>` tag. 
This means that `imgix` objects can be embedded into `tagList`s and other ui definitions that are built with the [`{htmltools}`] package.

```{r}
htmltools::div(
  imgix(2745224, mask = "ellipse", width = 400, height = 400),
  imgix('https://images.pexels.com/photos/45848/kumamoto-japan-aso-cloud-45848.jpeg', 
        mask = "ellipse", width = 400, height = 400)
)
```

This mode is currently used for all html-based rmarkdown formats.

#### Mode 3: image file

The image is downloaded to a local image and referenced via a local path.
For LaTeX-based rmarkdown formats.
To directly download an image, use `imgix_download()`

```r
imgix_download(imgix(2339009), file = "awesome_picture.jpeg")
```

## Palette

`imgix_palette()` allows you to extract the most dominant colors from an image.

```{r}
imgix_palette(2339009)
```

## Metadata

To get metadata about an image, use `imgix_meta()`

```{r}
imgix_meta(2422497)
```


## More examples

The rendering API exposes a lot of parameters that can be used to modify images.
All parameters to `imgix()` are directly sent as query parameters to the API.
See https://docs.imgix.com/apis/rendering for the full API documentation.

```{r}
imgix('https://ix-www.imgix.net/solutions/kingfisher.jpg',
       rect = '2100,600,1800,900')
imgix('https://assets.imgix.net/trim-ex4.jpg', monochrome = 787878)
imgix("https://images.unsplash.com/photo-1523712999610-f77fbcfc3843", 
       duotone = "000080,FA8072")
imgix(1048273, fit = "clip")
```

[imgix rendering API]: https://docs.imgix.com/apis/rendering
[`{htmlwidgets}`]: https://www.htmlwidgets.org/
[`{htmltools}`]: https://rstudio.github.io/htmltools/
[`{rmarkdown}`]: https://rmarkdown.rstudio.com/
[`{shiny}`]: https://shiny.rstudio.com/
[`{remotes}`]: https://remotes.r-lib.org/
