---
output: github_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(out.width = 800, out.height = 400)
```

# Imgixr

[`{htmlwidgets}`] bindings for the [imgix rendering API].
Use images from the API in your shiny apps and rmarkdown documents.

## Installation

This package can be installed directly from github using the `{remotes}` package

```r
remotes::install_github("GregorDeCillia/imgixr")
```

## Usage

Images can be defined with the `imgxr()` function.
You can either enter a full URL or an id from https://pexels.com.

```{r}
library(imgixr)
imgixr(2339009)
imgixr("https://images.unsplash.com/photo-1459478309853-2c33a60058e7")
```

## API Parameters

API parameters can be passed directly to `imgixr()`.
Underscores are automatically converted to hyphens.

```{r}
imgixr(2422497, rot = 30)
imgixr(1529360, txt = "Enjoy the rain", txt_size = 100, txt_color = "ddd", 
       txt_align = "center,middle", blur = 20)
```

## Shiny

Use `renderImgixr()` to include images to your shiny application.

```r
output$imgixr <- renderImgixr({
  imgixr_as_widget(imgixr(2339009))
})
```

The sizing must be defined in the corresponding output function `imgixrOutput()`.

## Rendering Modes

This packages uses three different strategies to render images depending on
the context. 

#### Mode 1: htmlwidget

The default mode.
The widget is shown using the [`{htmlwidgets}`] interface.
Typical usecases are shiny applications and the rstudio viewer pane.
Use `imgixr_as_widget()` to directly generate the widget object.

```{r}
widget <- imgixr_as_widget(imgixr(2339009))
```

#### Mode 2: html tag

The image is rendered to an html tag using the [`{htmltools}`] package.
The `htmltools::as.tag()` generic is implemented and returns an `<img>` tag. 
This means that `imgixr` objects can be embedded into `tagList`s and other ui definitions that are built with the [`{htmltools}`] package.

```r
htmltools::div(
  style = "background-color: #ddd; padding: 15px;",
  htmltools::h2("A nice image"),
  imgixr(2339009)
)
```

This mode is currently used for all html-based rmarkdown formats.

#### Mode 3: image file

The image is downloaded to a local image and referenced via a local path.
For LaTeX-based rmarkdown formats.
To directly download an image, use `imgixr_download()`

```r
imgixr_download(imgixr(2339009), file = "awesome_picture.jpeg")
```

## Metadata

To get metadata about an image, use `imgixr_meta()`

```{r}
imgixr_meta(2422497)
```


## More examples

```{r}
imgixr(2837863, sepia = 50, height = 800, fit = "clip")
imgixr(2745224, mask = "ellipse", width = 600, height = 600)
imgixr("https://images.unsplash.com/photo-1523712999610-f77fbcfc3843", 
       duotone = "000080,FA8072")
```

[imgix rendering API]: https://docs.imgix.com/apis/rendering
[`{htmlwidgets}`]: https://www.htmlwidgets.org/
[`{htmltools}`]: https://rstudio.github.io/htmltools/
